### 2018-01-15 circuit-elements/paper.tex
added observations

\input{header}
\physics
\begin{document}
\papertitle{Non-linear Circuit Elements}
\paperauth{A}{Khesin}{}
\paperauth{P}{Zavyalova}{}
\paperdate{January 17, 2018}
\begin{paperabs}

@@

	\paperfig{Hydrogen}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[outer]}
			\paperoline\papertableindexheader&\textsc{Scale}&\multirow{2}{*}{\textsc{Colour}}\\
			\papertablecheaderunit{.02}{\hspace{-0.5ex}}&\\\paperiline
			\papertableindex\papertablecval{7.26}\papertablecval{Red}\\\paperiline
			\papertableindex\papertablecval{11.80}\papertablecval{Blue-Green}\\\paperiline
			\papertableindex\papertablecval{15.15}\papertablecval{Violet}\\\paperiline
			\papertableindex\papertablecval{17.75}\papertablecval{Violet}\\\paperoline
		\end{papertable}\vspace{-1.5em}}
	{The scale readings and colours of the spectral lines of hydrogen.}\vspace{1em}

>>>>

\input{header}
\physics
\begin{document}
\papertitle{Non-linear Circuit Elements}
\paperauth{A}{Khesin}{}
\paperauth{P}{Zavyalova}{1002345036}
\paperdate{January 17, 2018}
\begin{paperabs}

@@

	The resistance of the thermistor at various temperatures was obtained and recorded. The uncertainty in resistance is taken to be the last digit increment in the least significant digit displayed.

	\paperfig{Thermistor}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[outer]}
			\paperoline\papertableindexheader&\textsc{Temperature}&\multirow{2}{*}{\textsc{Resistance}}\\
			\papertablecheaderunit{0.5}{\hspace{-0.5ex}}&\\\paperiline
			\papertableindex\papertablecval{352.5}\papertablecval{6.68}\\\paperiline
			\papertableindex\papertablecval{349.0}\papertablecval{6.93}\\\paperiline
			\papertableindex\papertablecval{348.0}\papertablecval{7.54}\\\paperiline
			\papertableindex\papertablecval{346.0}\papertablecval{8.01}\\\paperiline
			\papertableindex\papertablecval{340.0}\papertablecval{9.95}\\\paperiline
			\papertableindex\papertablecval{338.0}\papertablecval{10.33}\\\paperiline
			\papertableindex\papertablecval{335.0}\papertablecval{11.76}\\\paperiline
			\papertableindex\papertablecval{334.5}\papertablecval{12.36}\\\paperiline
			\papertableindex\papertablecval{329.5}\papertablecval{14.45}\\\paperiline
			\papertableindex\papertablecval{327.5}\papertablecval{15.33}\\\paperiline
			\papertableindex\papertablecval{324.0}\papertablecval{17.23}\\\paperiline
			\papertableindex\papertablecval{321.0}\papertablecval{19.51}\\\paperiline
			\papertableindex\papertablecval{319.0}\papertablecval{21.7}\\\paperiline
			\papertableindex\papertablecval{317.0}\papertablecval{24.3}\\\paperiline
			\papertableindex\papertablecval{314.0}\papertablecval{26.1}\\\paperiline
			\papertableindex\papertablecval{309.5}\papertablecval{31.4}\\\paperiline
			\papertableindex\papertablecval{308.5}\papertablecval{33.7}\\\paperiline
			\papertableindex\papertablecval{307.5}\papertablecval{35.5}\\\paperiline
			\papertableindex\papertablecval{305.0}\papertablecval{38.0}\\\paperiline
			\papertableindex\papertablecval{304.0}\papertablecval{40.3}\\\paperiline
			\papertableindex\papertablecval{301.5}\papertablecval{44.3}\\\paperiline
			\papertableindex\papertablecval{299.5}\papertablecval{47.7}\\\paperiline
			\papertableindex\papertablecval{298.0}\papertablecval{51.6}\\\paperiline
			\papertableindex\papertablecval{296.0}\papertablecval{56.3}\\\paperiline
			\papertableindex\papertablecval{294.0}\papertablecval{61.3}\\\paperiline
			\papertableindex\papertablecval{292.5}\papertablecval{66.9}\\\paperiline
			\papertableindex\papertablecval{290.5}\papertablecval{73.8}\\\paperiline
			\papertableindex\papertablecval{286.0}\papertablecval{92.9}\\\paperiline
			\papertableindex\papertablecval{283.0}\papertablecval{104.7}\\\paperiline
			\papertableindex\papertablecval{278.0}\papertablecval{126.2}\\\paperoline
		\end{papertable}\vspace{-1.5em}}
	{Resistance of thermistor at the given temperatures.}\vspace{1em}

	Further, current and potential for a tungsten filament light bulb were measured and recorded. The uncertainty is again taken to be the last digit increment in the least significant digit displayed.

	\paperfig{Light bulb}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[outer]}
			\paperoline\papertableindexheader&\multirow{2}{*}{\textsc{Potential}}&\multirow{2}{*}{\textsc{Current}}\\
			& \\ \paperiline
			\papertableindex\papertablecval{0.0222}\papertablecval{0.324}\\\paperiline
			\papertableindex\papertablecval{0.0776}\papertablecval{1.045}\\\paperiline
			\papertableindex\papertablecval{0.1122}\papertablecval{1.390}\\\paperiline
			\papertableindex\papertablecval{0.244}\papertablecval{2.27}\\\paperiline
			\papertableindex\papertablecval{0.472}\papertablecval{3.40}\\\paperiline
			\papertableindex\papertablecval{0.541}\papertablecval{3.69}\\\paperiline
			\papertableindex\papertablecval{0.697}\papertablecval{4.28}\\\paperiline
			\papertableindex\papertablecval{0.871}\papertablecval{4.89}\\\paperiline
			\papertableindex\papertablecval{1.128}\papertablecval{5.72}\\\paperiline
			\papertableindex\papertablecval{1.840}\papertablecval{7.68}\\\paperiline
			\papertableindex\papertablecval{1.940}\papertablecval{7.93}\\\paperiline
			\papertableindex\papertablecval{4.01}\papertablecval{12.34}\\\paperiline
			\papertableindex\papertablecval{6.00}\papertablecval{15.79}\\\paperiline
			\papertableindex\papertablecval{8.01}\papertablecval{18.83}\\\paperiline
			\papertableindex\papertablecval{10.24}\papertablecval{21.8}\\\paperiline
			\papertableindex\papertablecval{12.07}\papertablecval{24.1}\\\paperiline
			\papertableindex\papertablecval{14.27}\papertablecval{26.6}\\\paperiline
			\papertableindex\papertablecval{16.01}\papertablecval{28.5}\\\paperiline
			\papertableindex\papertablecval{17.98}\papertablecval{30.6}\\\paperiline
			\papertableindex\papertablecval{18.45}\papertablecval{31.1}\\\paperiline
			\papertableindex\papertablecval{19.86}\papertablecval{31.1}\\\paperiline
			\papertableindex\papertablecval{19.86}\papertablecval{32.5}\\\paperiline
			\papertableindex\papertablecval{21.0}\papertablecval{33.6}\\\paperiline
			\papertableindex\papertablecval{22.1}\papertablecval{34.6}\\\paperiline
			\papertableindex\papertablecval{22.9}\papertablecval{35.4}\\\paperiline
			\papertableindex\papertablecval{24.0}\papertablecval{36.4}\\\paperiline
			\papertableindex\papertablecval{25.1}\papertablecval{37.3}\\\paperoline
			\end{papertable}\vspace{-1.5em}}
	{Potential and current through the light bulb.}\vspace{1em}
